The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-20 cordillera-climate.tex
Update acknowledgements (Arjen and Constantine)

% Acknowledgements
\begin{acknowledgements}
We thank Ed Bueler and Andy Aschwanden for providing constant support on PISM and patiently answering our questions on the code internals, Laurent Brodeau and Soon-Heum Ko for assistance concerning software installations on supercomputing resources, and all PISM authors for providing the model open-source. Funding was provided by the Swedish Research Council (VR) to A. Stroeven (No. 2008-3449) and Stockholm University. Computer resources were provided by the Swedish National Infrastructure for Computing (SNIC) at the National Supercomputing Center (NSC) to A. Stroeven (No. 2013/1-145).

% Author contributions
\textit{Author contributions.}
J. Seguinot ran the simulations and wrote most of the paper; C. Khroulev implemented necessary code changes in PISM; I. Rogozhina helped with model set-up and experiment design; A. Stroeven initiated the Cordilleran Ice Sheet modelling project; and Q. Zhang prepared some of the forcing data. All authors contributed to the redaction.
\end{acknowledgements}

>>>>

% Acknowledgements
\begin{acknowledgements}
We thank Ed Bueler and Andy Aschwanden for providing constant support on PISM and patiently answering our questions on the code internals, Laurent Brodeau and Soon-Heum Ko for assistance concerning software installations on supercomputing resources, and all PISM authors for providing the model open-source. This work was supported by the Swedish Research Council (VR) grant \#2008-3449 to A. P. Stroeven and by NASA grant \#NNX13AM16G to E. Bueler. Computer resources were provided by the Swedish National Infrastructure for Computing (SNIC) allocation \#2013/1-145 to A. P. Stroeven at the National Supercomputing Center (NSC).

% Author contributions
\textit{Author contributions.}
J. Seguinot ran the simulations and wrote most of the paper; C. Khroulev implemented necessary code changes in PISM; I. Rogozhina helped with model set-up and experiment design; A. P. Stroeven initiated the Cordilleran Ice Sheet modelling project; and Q. Zhang prepared some of the forcing data. All authors contributed to paper writing.
\end{acknowledgements}
